Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2019-11-03 PaperMagneticProfiles_JBSMSE.tex
Cite our Trade-offs paper to justify accounting of irreversibilities.

\textcolor{blue}{As pointed out in \colorbox{yellow}{citar o paper da ATE - Design trade-offs}, since external sources of irreversibility (e.g., heat transfer with a finite temperature difference in the heat exchangers) are ignored and no eddy currents and hysteresis losses are present,} the magnetic power required to \textcolor{blue}{magnetize the solid refrigerant and produce the MCE} in the AMR cycle is given by the product of the Carnot efficiency and the cooling capacity as follows:

>>>>

As pointed out in \cite{bib:fortkamp20-desig}, since external sources of irreversibility (e.g., heat transfer with a finite temperature difference in the heat exchangers) are ignored and no eddy currents and hysteresis losses are present, the magnetic power required to magnetize the solid refrigerant and produce the MCE in the AMR cycle is given by the product of the Carnot efficiency and the cooling capacity as follows:
